The Small World Network Effect in Open Source Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-16 paper/main.tex
A few more references.

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{positioning}
\setlength{\abovecaptionskip}{2pt}

@@

\textit{Graph Structure}
A bipartite graph is a specialized type of graph containing two disjoint sets of verticies. This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$. For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors. Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}. This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.

@@

One of the main sources of information loss is multiple connections between projects, or projects that share multiple collaborators. When doing a bipartite projection based on projects $P$, a single link could represent one shared developer or many. This is an evident source of data loss in the projection. The simple approach is to treat one connection the same as many connections between nodes. This is straightforward but lossy\cite{zhou2007bipartite,grossman1995portion}. A better approach is to assign a \textit{weight} to each edge representing repeated links -- or in our case -- multiple shared collaborators\cite{zha2001bipartite}.

@@

We calcluate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

Also, measuring \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. For example

@@

\textit{Small-World-ness}

@@

>>>>

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{positioning}
\setlength{\abovecaptionskip}{2pt}
\setcounter{secnumdepth}{2}

@@

\subsubsection{Graph Structure}
A bipartite graph is a specialized type of graph containing two disjoint sets of verticies. This can be denoted by ${G=(P,C,E)}$, where ${P \cap C = \emptyset}$. For our purposes, let set $P$ be the set of all projects, and set $C$ be the set of all contributors. Each project node, therefore, is only connected to contributor nodes, and vice versa, as show in figure \ref{fig:example_bipartite_graph}. This bipartite representation is typical of what is found in social and collaboration networks\cite{ramasco2004self}.

@@

One of the main sources of information loss is multiple connections between projects, or projects that share multiple collaborators. When doing a bipartite projection based on projects $P$, a single link could represent one shared developer or many. This is a source of data loss in the projection. The simple approach is to treat one connection the same as many connections between nodes. This is straightforward but lossy\cite{zhou2007bipartite,grossman1995portion}. A better approach is to assign a \textit{weight} to each edge representing repeated links -- or in our case -- multiple shared collaborators\cite{zha2001bipartite,barrat2004architecture}.

@@

\subsubsection{Graph Analysis}
To support our hypotheses, there are several key metrics to be studied in regards to the aforementioned graph. Many of these metrics follow the work of Boccaletti \textit{et. al}\cite{boccaletti2006complex}, and other studies of similar graph types CITATION HERE.

\textit{Clustering Coefficient (Transitivity}\\
We calculate the \textit{Clustering Coefficient} (or $C^\Delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

\textit{Clustering Coefficient (Average}\\
Another approach to clustering is to take the average of each node's local clustering coefficient\cite{watts1998collective}.

\[ c_i = \frac{|\{e_{jk}\}|}{k_i(k_i-1)} :\, v_j,v_k \in N_i,\, e_{jk} \in E \]

{$N_i = \{v_j : e_{ij} \in E\}$}

\textit{Average Path Length}\\
Also, calculating the \textit{Path Length} ($L$) allows us to determine how far removed developers in the graph are from one another. The path length is calculated as the average distance between any two node pairs in the graph:

\[L = \frac{1}{|P| \cdot (|P|-1)} \sum_{i \neq j}\lambda(v_i,v_j)\]

Where {$v_i \in P$}, {$v_j \in P$}, and {$\lambda(v_i,v_j)$} denotes the shortest path between the two nodes. We only consider path length for connected subgraphs, avoiding some complexities of this calculation on disconnected graphs\cite{boccaletti2006complex}.

@@

\textit{Small-World-ness}\\

@@

\subsubsection{Qualitative Analysis}
It has been well recognized through history that people tend to make connections with people with whom they share similarities\cite{mcpherson2001birds}.
